A generalized framework for urban typology prototype generation for agent-based simulations in SimMobility

### 2018-01-09 manuscript/manuscript.tex
changed title
updates to manuscript

\title{Prototype city generation for mobility simulation in urban typologies: a  generalized framework}
\author{}
\maketitle

@@

    \node[res] (assig) [below right= of locwe] {{\bf Assignment}\\{\footnotesize IND$\to$WORK|EDU}};

>>>>

\title{A generalized framework for urban typology prototype generation for agent-based simulations in SimMobility}
\author{Jimi Oke \and Iveel Tsogsuren \and Youssef Medhat \and Carlos Lima Azevedo \and Chris Zegras \and Joseph Ferreria \and Moshe Ben-Akiva}

\maketitle

@@

    \node[res] (assig) [below =4cm of landu] {{\bf Assignment}\\{\footnotesize IND$\to$WORK|EDU}};
